\textit{Supplementary materials for}: Feature and order manipulations in a free recall task affect memory for current and future lists

### 2023-01-24 paper/supplement.tex

    \caption{\textbf{Recall accuracy by study list number.}  Each panel displays the average recall accuracy (across participants) as a function of the number of studied lists for the
    random conditions (\textbf{A.}), order manipulation conditions (\textbf{B.}), and adaptive conditions (\textbf{C.}).  The conditions are denoted by color.  Note that the first four
    lists in all of the ``adaptive'' conditions were ordered randomly to compute a baseline fingerprint for each participant prior to initiating the adaptive ordering procedure.  All error
    ribbons denote bootstrap-estimated 95\% confidence intervals, calculated across participants.}
        \label{fig:accuracy-by-list}
\end{figure}

@@

    \caption{\textbf{Memory ``fingerprints'' (random conditions).}
    The across-participant distributions of clustering scores for each feature
    type ($x$-coordinate) are displayed for each experimental condition
    (color), separately for early (top) and late (bottom) lists.}
        \label{fig:fingerprints-random}
\end{figure}

@@

    \caption{\textbf{Memory ``fingerprints'' (adaptive conditions).}
    The across-participant distributions of clustering scores for each feature
    type ($x$-coordinate) are displayed for each experimental condition
    (color).}
        \label{fig:fingerprints-adaptive}
\end{figure}

@@

    \caption{\textbf{Probability of $n$\textsuperscript{th} recall matrices.}  Each sub-panel displays
    the average probability of recalling the given word (Presentation position, $x$-coordinate)
    at the given output position ($y$-coordinate); color denotes the probability.  \textbf{A. Random conditions.}  The top rows
    display data from early (order manipulation) lists, the middle rows display data from late (randomly ordered)
    lists, and the bottom rows display the differences between the matrices in the top and middle rows.  Panel columns denote experimental conditions.
    \textbf{B. Order manipulation conditions.}  The matrices are displayed in the same format as those in Panel A.
    Panel columns are organized by feature type (semantic, lexicographic, or visual).  \textbf{C. Adaptive conditions.}
    The sub-panels are displayed in the same formats as Panels A and B, but here the matrices
    and contrasts (indicated in $y$-axis labels) reflect different list manipulation conditions.}

>>>>

\caption{\textbf{Recall accuracy by study list number.} Each panel displays the
average recall accuracy (across participants) as a function of the number of
studied lists for the random conditions (\textbf{A.}), order manipulation
conditions (\textbf{B.}), and adaptive conditions (\textbf{C.}). The conditions
are denoted by color. Note that the first four lists in all of the ``adaptive''
conditions were ordered randomly to compute a baseline fingerprint for each
participant prior to initiating the adaptive ordering procedure. \textbf{All
panels.} All error ribbons denote bootstrap-estimated 95\% confidence
intervals, calculated across participants.} 
\label{fig:accuracy-by-list}

@@

    \caption{\textbf{Memory ``fingerprints'' (random conditions).}
    The across-participant distributions of clustering scores for each feature
    type ($x$-axis) are displayed for each experimental condition
    (color), separately for early (top) and late (bottom) lists.}
        \label{fig:fingerprints-random}
\end{figure}

@@

    \caption{\textbf{Memory ``fingerprints'' (adaptive conditions).}
    The across-participant distributions of clustering scores for each feature
    type ($x$-axis) are displayed for each experimental condition
    (color).}
        \label{fig:fingerprints-adaptive}
\end{figure}

@@

    \caption{\textbf{Probability of $n$\textsuperscript{th} recall matrices.}
    Each sub-panel displays the average probability of recalling the given word
    (Presentation position, matrix column) at the given output position (matrix
    row); color denotes the probability. \textbf{A. Random conditions.} The top
    rows of matrices display data from early (order manipulation) lists, the
    middle rows of matrices display data from late (randomly ordered) lists,
    and the bottom rows of matrices display the differences between the
    matrices in the top and middle rows. Panel columns denote experimental
    conditions. \textbf{B. Order manipulation conditions.} The matrices are
    displayed in the same format as those in Panel A. Panel columns are
    organized by feature type (semantic, lexicographic, or visual). \textbf{C.
    Adaptive conditions.} The sub-panels are displayed in the same formats as
    Panels A and B, but here the matrices and contrasts (indicated in $y$-axis
    labels) reflect different list manipulation conditions.}
